Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-17 paper_knowledge.tex
Added biographies

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section*{Biographies}

\subsection*{Séverin Lemaignan}

Séverin Lemaignan received the M.S. degree in mechanical engineering from the
École des Arts et Métiers, Paris, France and the Technical University of
Karlsruhe, Germany.  After working for a year as research engineer in mobile
robotics at INRIA, he is now Ph.D student at LAAS-CNRS, Toulouse, France and
Munich Technical University, Germany. He mainly works on knowledge
representation for cognitive robotic architectures, natural human-robot
interaction and high-level robotic simulation.

\subsection*{Raquel Ros}

Raquel Ros is a Marie-Curie fellow at the Robotics and Interactions Group in
LAAS-CNRS, where she focuses on implementation of cognitive models for social
robots, knowledge grounding and enhancement of human-robot interaction. She
received her PhD in computer science from the Universitat Autònoma de Barcelona
in 2008. She was then awarded with a Marie-Curie fellowship and joined
LAAS-CNRS. Her main research interests are decision-making, cognitive models
for social robotics and long-term interaction.

\subsection*{E. Akin Sisbot}

Emrah Akin Sisbot received the B.S. degree in computer engineering from
Galatasaray University, Istanbul, Turkey, in 2003 and the M.S. degree in
artificial intelligence from the University Paul Sabatier, Toulouse, France, in
2004. In 2008 he received his Ph.D degree from University of Toulouse with his
research on Human-Aware Motion Planning. Until 2011 he was a Postdoc in
Robotics and Interactions Group in LAAS-CNRS where he focused on Spatial
Reasoning and Knowledge Management. He recently joined to University of
Washington as a Research Associate, where he works on Interactive RGB-D SLAM
and robot navigation. His research interests include motion planning,
human-robot interaction, spatial reasoning and mapping.

\subsection*{Rachid Alami}

Rachid Alami received a Docteur-Ingénieur degree in 1983 in computer science
from the Institut National Polytechnique de Toulouse and the ``Habilitation à
Diriger des Recherches'' in 1996 from Paul Sabatier University. He joined the
Robotics and Artificial Intelligence group at LAAS-CNRS, Toulouse, France in
1980. He is now a Senior Research Scientist and the head of Robotics and
InteractionS group at LAAS-CNRS. His current research interests include the
study of control architectures for autonomous robots, task and motion planning,
multi-robot cooperation, personal robots, and human-robot interaction.

\subsection*{Michael Beetz}

Michael Beetz received his diploma degree in Computer Science with distinction
from the University of Kaiserslautern. He received his MSc, MPhil, and PhD
degrees from Yale University in 1993, 1994, and 1996 and his Venia Legendi from
the University of Bonn in 2000. Michael Beetz was a member of the steering
committee of the European network of excellence in AI planning (PLANET) and
coordinating the research area ``robot planning''. He is associate editor of
the AI Journal. His research interests include plan-based control of robotic
agents, knowledge processing and representation for robots, integrated robot
learning, and cognitive perception.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\end{document}
